QALY Comparison - Living Wage Intervention

### 2023-11-10 minos/testing/QALY_comparison_energyCrises.Rmd
Point to the right location for qaly outputs, remove some debugging stuff from earlier

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

@@

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qaly_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_noSupport.csv'))

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')

@@

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))

### 2023-11-10 minos/testing/QALY_comparison_livingWage.Rmd
Point to the right location for qaly outputs, remove some debugging stuff from earlier

```{r}
# # read in QALY files for baseline and interventions
# out.path <- here::here('output', 'default_config')
# #out.path <- here::here('output', 'glasgow_scaled')
# 
# base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
# wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))
# 
# base <- read.csv(paste0(base.path, 'qalys.csv'))
# wage <- read.csv(paste0(wage.path, 'qalys.csv'))

out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'

base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
wage.path <- get_latest_runtime_subdirectory(here::here(out.path, 'livingWageIntervention'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
wage <- read.csv(paste0(wage.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
# wage <- read.csv(paste0(out.path, 'qalys_livwage.csv'))
